---
output: pdf_document
---
```{r include_packages_2, include = FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis and also two functions
# used for labeling and referencing
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(dplyr))
    install.packages("dplyr", repos = "http://cran.rstudio.com")
if(!require(ggplot2))
    install.packages("ggplot2", repos = "http://cran.rstudio.com")
if(!require(ggplot2))
    install.packages("bookdown", repos = "http://cran.rstudio.com")
if(!require(thesisdown)){
  library(devtools)
  devtools::install_github("ismayc/thesisdown")
  }
library(thesisdown)
load("data/d1.Rda")
```


```{r codes, include=FALSE}
outcome <- d1[,2]
player <- d1[,3]
rank <- d1[,4]
battle_length <- d1[,5]
switches <- d1[,6]
stealthrockcount <- d1[,7]
spikescount <- d1[,8]
toxspikecount <- d1[,9]
stickywebcount <- d1[,10]
defogcount <- d1[,11]
rapidspincount <- d1[,12]
dragontailcount <- d1[,13]
roarcount <- d1[,14]
whirlwindcount  <- d1[,15]
sp2 <- spikescount^2 
toxsp2 <- toxspikecount^2
whirl2 <- whirlwindcount^2
dt2 <- whirlwindcount^2
roar2  <-whirlwindcount^2
fog2 <- defogcount^2
rapid2 <- rapidspincount^2
Abomasnow <- d1[,16]
Absol<- d1[,17]
Accelgor<- d1[,18]
Aerodactyl<- d1[,19]
Aggron<- d1[,20]
Alakazam<- d1[,21]
Alomomola<- d1[,22]
Altaria<- d1[,23]
Ambipom<- d1[,24]
Amoonguss<- d1[,25]
Ampharos<- d1[,26]
Arbok<- d1[,27]
Arcanine<- d1[,28]
Archeops<- d1[,29]
Ariados<- d1[,30]
Armaldo<- d1[,31]
Aromatisse<- d1[,32]
Articuno<- d1[,33]
Audino<- d1[,34]
Aurorus<- d1[,35]
Avalugg<- d1[,36]
Azelf<- d1[,37]
Azumarill<- d1[,38]
Banette<- d1[,39]
Barbaracle<- d1[,40]
Basculin<- d1[,41]
Bastiodon<- d1[,42]
Beartic<- d1[,43]
Beautifly<- d1[,44]
Beedrill<- d1[,45]
Beheeyem<- d1[,46]
Bellossom<- d1[,47]
Bibarel<- d1[,48]
Bisharp<- d1[,49]
Blastoise<- d1[,50]
Blissey<- d1[,51]
Bouffalant<- d1[,52]
Braviary<- d1[,53]
Breloom<- d1[,54]
Bronzong<- d1[,55]
Butterfree<- d1[,56]
Cacturne<- d1[,57]
Camerupt<- d1[,58]
Carbink<- d1[,59]
Carnivine<- d1[,60]
Carracosta<- d1[,61]
Castform<- d1[,62]
Celebi<- d1[,63]
Chandelure<- d1[,64]
Chansey<- d1[,65]  
Charizard<- d1[,66]  
Chatot<- d1[,67]  
Cherrim<- d1[,68]  
Chesnaught<- d1[,69]  
Chimecho<- d1[,70]  
Cinccino<- d1[,71]  
Clawitzer<- d1[,72]  
Claydol<- d1[,73]  
Clefable<- d1[,74]  
Clefairy<- d1[,75]  
Cloyster<- d1[,76]  
Cobalion<- d1[,77]  
Cofagrigus<- d1[,78]  
Combusken<- d1[,79]  
Conkeldurr<- d1[,80]  
Corsola<- d1[,81]  
Cradily<- d1[,82]  
Crawdaunt<- d1[,83]  
Cresselia<- d1[,84]  
Crobat<- d1[,85]  
Crustle<- d1[,86]  
Cryogonal<- d1[,87]  
Darmanitan<- d1[,88]  
Dedenne<- d1[,89]  
Delcatty<- d1[,90]  
Delibird<- d1[,91]  
Delphox<- d1[,92]  
Dewgong<- d1[,93]  
Diancie<- d1[,94]  
Diggersby<- d1[,95]  
Ditto<- d1[,96]  
Dodrio<- d1[,97]  
Donphan<- d1[,98]  
Doublade<- d1[,99]  
Dragalge<- d1[,100]  
Dragonair<- d1[,101]  
Dragonite<- d1[,102]  
Drapion<- d1[,103]  
Drifblim<- d1[,104]  
Druddigon<- d1[,105]  
Dugtrio<- d1[,106]  
Dunsparce<- d1[,107]  
Duosion<- d1[,108]  
Durant<- d1[,109]  
Dusclops<- d1[,110]  
Dusknoir<- d1[,111]  
Dustox<- d1[,112]  
Eelektross<- d1[,113]  
Electivire<- d1[,114]  
Electrode<- d1[,115]  
Emboar<- d1[,116]  
Emolga<- d1[,117]  
Empoleon<- d1[,118]  
Entei<- d1[,119]  
Escavalier<- d1[,120]  
Espeon<- d1[,121]  
Excadrill<- d1[,122]  
Exeggutor<- d1[,123]  
Exploud<- d1[,124]  
Farfetchd<- d1[,125]  
Fearow<- d1[,126]  
Feraligatr<- d1[,127]  
Ferroseed<- d1[,128]  
Ferrothorn<- d1[,129]  
Flareon<- d1[,130]  
Fletchinder<- d1[,131]  
Floatzel<- d1[,132]  
Florges<- d1[,133]  
Flygon<- d1[,134]  
Forretress<- d1[,135]  
Fraxure<- d1[,136]  
Froslass<- d1[,137]  
Furfrou<- d1[,138]  
Furret<- d1[,139]  
Gabite<- d1[,140]  
Gallade<- d1[,141]  
Galvantula<- d1[,142]  
Garbodor<- d1[,143]  
Garchomp<- d1[,144]  
Gardevoir<- d1[,145]  
Gastrodon<- d1[,146]  
Gengar<- d1[,147]  
Gigalith<- d1[,148]  
Girafarig<- d1[,149]  
Glaceon<- d1[,150]  
Glalie<- d1[,151]  
Gligar<- d1[,152]  
Gliscor<- d1[,153]  
Gogoat<- d1[,154]  
Golbat<- d1[,155]  
Golduck<- d1[,156]  
Golem<- d1[,157]  
Golurk<- d1[,158]  
Goodra<- d1[,159]  
Gorebyss<- d1[,160]  
Gothitelle<- d1[,161]  
Gourgeist<- d1[,162]  
Granbull<- d1[,163]  
Grumpig<- d1[,164]  
Gurdurr<- d1[,165]  
Gyarados<- d1[,166]  
Hariyama<- d1[,167]  
Haunter<- d1[,168]  
Hawlucha<- d1[,169]  
Haxorus<- d1[,170]  
Heatmor<- d1[,171]  
Heatran<- d1[,172]  
Heliolisk<- d1[,173]  
Heracross<- d1[,174]  
Hippowdon<- d1[,175]  
Hitmonchan<- d1[,176]  
Hitmonlee<- d1[,177]  
Hitmontop<- d1[,178]  
Honchkrow<- d1[,179]  
Hoopa<- d1[,180]  
HoopaU<- d1[,181]  
Houndoom<- d1[,182]  
Huntail<- d1[,183]  
Hydreigon<- d1[,184]  
Hypno<- d1[,185]  
Illumise<- d1[,186]  
Infernape<- d1[,187]  
Jellicent<- d1[,188]  
Jirachi<- d1[,189]  
Jolteon<- d1[,190]  
Jumpluff<- d1[,191]  
Jynx<- d1[,192]  
Kabutops<- d1[,193]  
Kadabra<- d1[,194]  
Kangaskhan<- d1[,195]  
Kecleon<- d1[,196]  
Keldeo<- d1[,197]  
Kingdra<- d1[,198]  
Kingler<- d1[,199]  
Klang<- d1[,200]  
Klefki<- d1[,201]  
Klinklang<- d1[,202]  
Kricketune<- d1[,203]  
Krokorok<- d1[,204]  
Krookodile<- d1[,205]  
Kyurem<- d1[,206]  
KyuremB<- d1[,207]  
LandorusT<- d1[,208]  
Lanturn<- d1[,209]  
Lapras<- d1[,210]  
Latias<- d1[,211]  
Latios<- d1[,212]  
Leafeon<- d1[,213]  
Leavanny<- d1[,214]  
Ledian<- d1[,215]  
Lickilicky<- d1[,216]  
Liepard<- d1[,217]  
Lilligant<- d1[,218]  
Linoone<- d1[,219]  
Lopunny<- d1[,220]  
Lucario<- d1[,221]  
Ludicolo<- d1[,222]  
Lumineon<- d1[,223]  
Lunatone<- d1[,224]  
Luvdisc<- d1[,225]  
Luxray<- d1[,226]  
Machamp<- d1[,227]  
Machoke<- d1[,228]  
Magcargo<- d1[,229]  
Magmortar<- d1[,230]  
Magneton<- d1[,231]  
Magnezone<- d1[,232]  
Malamar<- d1[,233]  
Mamoswine<- d1[,234]  
Manaphy<- d1[,235]  
Mandibuzz<- d1[,236]  
Manectric<- d1[,237]  
Mantine<- d1[,238]  
Maractus<- d1[,239]  
Marowak<- d1[,240]  
Masquerain<- d1[,241]  
Mawile<- d1[,242]  
Medicham<- d1[,243]  
Meganium<- d1[,244]  
Meloetta<- d1[,245]  
Meowstic<- d1[,246]  
Mesprit<- d1[,247]  
Metagross<- d1[,248]  
Metang<- d1[,249]  
Mew<- d1[,250]  
Mienshao<- d1[,251]  
Mightyena<- d1[,252]  
Milotic<- d1[,253]  
Miltank<- d1[,254]  
Minun<- d1[,255]  
Misdreavus<- d1[,256]  
Mismagius<- d1[,257]  
Moltres<- d1[,258]  
Monferno<- d1[,259]  
Mothim<- d1[,260]  
MrMime<- d1[,261]  
Muk<- d1[,262]  
Murkrow<- d1[,263]  
Musharna<- d1[,264]  
Nidoking<- d1[,265]  
Nidoqueen<- d1[,266]  
Ninetales<- d1[,267]  
Ninjask<- d1[,268]  
Noctowl<- d1[,269]  
Noivern<- d1[,270]  
Octillery<- d1[,271]  
Omastar<- d1[,272]  
Pachirisu<- d1[,273]  
Pangoro<- d1[,274]  
Parasect<- d1[,275]  
Pawniard<- d1[,276]  
Pelipper<- d1[,277]  
Persian<- d1[,278]  
Phione<- d1[,279]  
Pidgeot<- d1[,280]  
Piloswine<- d1[,281]  
Pinsir<- d1[,282]  
Plusle<- d1[,283]  
Politoed<- d1[,284]  
Poliwrath<- d1[,285]  
PorygonZ<- d1[,286]  
Porygon2<- d1[,287]  
Primeape<- d1[,288]  
Prinplup<- d1[,289]  
Probopass<- d1[,290]  
Purugly<- d1[,291]  
Pyroar<- d1[,292]  
Quagsire<- d1[,293]  
Quilladin<- d1[,294]  
Qwilfish<- d1[,295]  
Raichu<- d1[,296]  
Raikou<- d1[,297]  
Rampardos<- d1[,298]  
Rapidash<- d1[,299]  
Raticate<- d1[,300]  
Regice<- d1[,301]  
Regigigas<- d1[,302]  
Regirock<- d1[,303]  
Registeel<- d1[,304]  
Relicanth<- d1[,305]  
Reuniclus<- d1[,306]  
Rhydon<- d1[,307]  
Rhyperior<- d1[,308]  
Roselia<- d1[,309]  
Roserade<- d1[,310]  
Rotom<- d1[,311]  
RotomC<- d1[,312]  
RotomF<- d1[,313]  
RotomH<- d1[,314]  
RotomS<- d1[,315]  
RotomW<- d1[,316]  
Sableye<- d1[,317]  
Salamence<- d1[,318]  
Samurott<- d1[,319]  
Sandslash<- d1[,320]  
Sawk<- d1[,321]  
Sawsbuck<- d1[,322]  
Sceptile<- d1[,323]  
Scizor<- d1[,324]  
Scolipede<- d1[,325]  
Scrafty<- d1[,326]  
Scyther<- d1[,327]  
Seaking<- d1[,328]  
Seismitoad<- d1[,329]  
Serperior<- d1[,330]  
Servine<- d1[,331]  
Seviper<- d1[,332]  
Sharpedo<- d1[,333]  
Shaymin<- d1[,334]  
Shedinja<- d1[,335]  
Shiftry<- d1[,336]  
Shuckle<- d1[,337]  
Sigilyph<- d1[,338]  
Simipour<- d1[,339]  
Simisage<- d1[,340]  
Simisear<- d1[,341]  
Skarmory<- d1[,342]  
Skuntank<- d1[,343]  
Slaking<- d1[,344]  
Slowbro<- d1[,345]  
Slowking<- d1[,346]  
Slurpuff<- d1[,347]  
Smeargle<- d1[,348]  
Sneasel<- d1[,349]  
Snorlax<- d1[,350]  
Solrock<- d1[,351]  
Spinda<- d1[,352]  
Spiritomb<- d1[,353]  
Stantler<- d1[,354]  
Staraptor<- d1[,355]  
Starmie<- d1[,356]  
Steelix<- d1[,357]  
Stoutland<- d1[,358]  
Stunfisk<- d1[,359]  
Sudowoodo<- d1[,360]  
Suicune<- d1[,361]  
Sunflora<- d1[,362]  
Swalot<- d1[,363]  
Swampert<- d1[,364]  
Swanna<- d1[,365]  
Swellow<- d1[,366]  
Swoobat<- d1[,367]  
Sylveon<- d1[,368]  
Talonflame<- d1[,369]  
Tangela<- d1[,370]  
Tangrowth<- d1[,371]  
Tauros<- d1[,372]  
Tentacruel<- d1[,373]  
Terrakion<- d1[,374]  
Throh<- d1[,375]  
Thundurus<- d1[,376]  
ThundurusT<- d1[,377]  
Togekiss<- d1[,378]  
Togetic<- d1[,379]  
Torkoal<- d1[,380]  
Tornadus<- d1[,381]  
TornadusT<- d1[,382]  
Torterra<- d1[,383]  
Toxicroak<- d1[,384]  
Trevenant<- d1[,385]  
Tropius<- d1[,386]  
Typhlosion<- d1[,387]  
Tyranitar<- d1[,388]  
Tyrantrum<- d1[,389]  
Umbreon<- d1[,390]  
Unfezant<- d1[,391]  
Unown<- d1[,392]  
Ursaring<- d1[,393]  
Uxie<- d1[,394]  
Vanilluxe<- d1[,395]  
Vaporeon<- d1[,396]  
Venomoth<- d1[,397]  
Venusaur<- d1[,398]  
Vespiquen<- d1[,399]  
Vibrava<- d1[,400]  
Victini<- d1[,401]  
Victreebel<- d1[,402]  
Vigoroth<- d1[,403]  
Vileplume<- d1[,404]  
Virizion<- d1[,405]  
Vivillon<- d1[,406]  
Volbeat<- d1[,407]  
Volcarona<- d1[,408]  
Vullaby<- d1[,409]  
Wailord<- d1[,410]  
Walrein<- d1[,411]  
Wartortle<- d1[,412]  
Watchog<- d1[,413]  
Weavile<- d1[,414]  
Weezing<- d1[,415]  
Whimsicott<- d1[,416]  
Whiscash<- d1[,417]  
Wigglytuff<- d1[,418]  
Wobbuffet<- d1[,419]  
Wormadam<- d1[,420]  
WormadamSandy<- d1[,421]  
WormadamTrash<- d1[,422]  
Xatu<- d1[,423]  
Yanmega<- d1[,424]  
Zangoose <- d1[,425]    
Zapdos<- d1[,426]
Zebstrika<- d1[,427]
Zoroark<- d1[,428]
Zweilous<- d1[,429]
Zygarde<- d1[,430]
Abomasite <- d1[,431]
Absolite <- d1[,431]
Aerodactylite <- d1[,432]
Aggronite <- d1[,433]
Alakazite <- d1[,434]
Altarianite <- d1[,435]
Ampharosite <- d1[,436]
Audinite <- d1[,437]
Banettite <- d1[,438]
Beedrillite <- d1[,439]
Blastoisinite <- d1[,441]
Cameruptite <- d1[,442]
Charizarditex <- d1[,443]
Charizarditey <- d1[,444]
Diancite <- d1[,445]
Galladite <- d1[,446] 
Garchompite <- d1[,447]
Gardevoirite <- d1[,448]
Glalitite <- d1[,449]
Gyaradosite <- d1[,450]
Heracronite <- d1[,451]
Houndoominite <- d1[,452]
Latiasite <- d1[,453]
Latiosite <- d1[,454]
Lopunnite <- d1[,455]
Manectite <- d1[,456]
Medichamite <- d1[,457]
Metagrossite <- d1[,458]
Pidgeotite <- d1[,459]
Pinsirite <- d1[,460]
Sablenite <- d1[,461]
Sceptilite <- d1[,462]
Scizorite <- d1[,463]
Sharpedonite <- d1[,464]
Slowbronite <- d1[,465]
Steelixite <- d1[,466]
Swampertite <- d1[,467]
Tyranitarite <- d1[,468]
Venusaurite <- d1[,469]
stAerodactyl         <- stealthrockcount*Aerodactyl
  stAggron           <- stealthrockcount*Aggron
  stArcheops          <- stealthrockcount*Archeops       
  stArmaldo           <- stealthrockcount*Armaldo
  stAurorus           <- stealthrockcount*Aurorus
  stAzelf              <- stealthrockcount*Azelf     
  stBarbaracle          <- stealthrockcount*Barbaracle          
  stBastiodon            <- stealthrockcount*Bastiodon          
  stBibarel               <- stealthrockcount*Bibarel      
  stBisharp                <- stealthrockcount*Bisharp      
  stBlissey                 <- stealthrockcount*Blissey      
  stBronzong                 <- stealthrockcount*Bronzong   
  stCamerupt                  <- stealthrockcount*Camerupt    
  stCarbink                    <- stealthrockcount*Carbink        
  stCarracosta               <- stealthrockcount*Carracosta
  stCelebi                    <- stealthrockcount*Celebi  
  stChansey                    <- stealthrockcount*Chansey       
  stClaydol                     <- stealthrockcount*Claydol
  stClefable                     <- stealthrockcount*Clefable 
  stClefairy                      <- stealthrockcount*Clefairy     
  stCobalion                 <- stealthrockcount*Cobalion
  stCorsola                   <- stealthrockcount*Corsola  
  stCradily                    <- stealthrockcount*Cradily        
  stCrustle                   <- stealthrockcount*Crustle
  stDiancie                <- stealthrockcount*Diancie  
  stDonphan                 <- stealthrockcount*Donphan           
  stDruddigon                <- stealthrockcount*Druddigon
  stDugtrio                   <- stealthrockcount*Dugtrio   
  stDunsparce                  <- stealthrockcount*Dunsparce        
  stEmpoleon                   <- stealthrockcount*Empoleon
  stExcadrill                   <- stealthrockcount*Excadrill   
  stFerroseed                    <- stealthrockcount*Ferroseed      
  stFerrothorn                <- stealthrockcount*Ferrothorn
  stForretress                 <- stealthrockcount*Forretress    
  stGabite                      <- stealthrockcount*Gabite      
  stGarchomp                  <- stealthrockcount*Garchomp
  stGigalith                   <- stealthrockcount*Gigalith   
  stGligar                      <- stealthrockcount*Gligar       
  stGliscor                   <- stealthrockcount*Gliscor
  stGolem                      <- stealthrockcount*Golem 
  stGolurk                      <- stealthrockcount*Golurk       
  stHeatran                    <- stealthrockcount*Heatran
  stHippowdon                   <- stealthrockcount*Hippowdon   
  stInfernape                    <- stealthrockcount*Infernape  
  stJirachi                   <- stealthrockcount*Jirachi
  stKabutops                   <- stealthrockcount*Kabutops   
  stKecleon                     <- stealthrockcount*Kecleon       
  stKrokorok                  <- stealthrockcount*Krokorok
  stKrookodile                 <- stealthrockcount*Krookodile    
  stLunatone                    <- stealthrockcount*Lunatone   
  stMagcargo                <- stealthrockcount*Magcargo
  stMamoswine                <- stealthrockcount*Mamoswine     
  stMarowak                   <- stealthrockcount*Marowak         
  stMawile                    <- stealthrockcount*Mawile
  stMesprit                    <- stealthrockcount*Mesprit 
  stMetagross                   <- stealthrockcount*Metagross   
  stMetang                <- stealthrockcount*Metang
  stMew                    <- stealthrockcount*Mew   
  stMiltank                 <- stealthrockcount*Miltank          
  stMonferno             <- stealthrockcount*Monferno
  stNidoking              <- stealthrockcount*Nidoking         
  stNidoqueen              <- stealthrockcount*Nidoqueen    
  stOmastar                 <- stealthrockcount*Omastar   
  stPawniard                 <- stealthrockcount*Pawniard      
  stPiloswine                 <- stealthrockcount*Piloswine     
  stPinsir                     <- stealthrockcount*Pinsir 
  stPrinplup                    <- stealthrockcount*Prinplup   
  stProbopass                    <- stealthrockcount*Probopass  
  stRampardos                 <- stealthrockcount*Rampardos
  stRegirock                   <- stealthrockcount*Regirock    
  stRegisteel                   <- stealthrockcount*Registeel   
  stRelicanth                  <- stealthrockcount*Relicanth
  stRhydon                      <- stealthrockcount*Rhydon 
  stRhyperior                    <- stealthrockcount*Rhyperior  
  stSandslash                   <- stealthrockcount*Sandslash
  stSeismitoad                    <- stealthrockcount*Seismitoad 
  stShuckle                        <- stealthrockcount*Shuckle   
  stSkarmory                 <- stealthrockcount*Skarmory
  stSolrock                   <- stealthrockcount*Solrock    
  stSteelix                    <- stealthrockcount*Steelix       
  stStunfisk                    <- stealthrockcount*Stunfisk 
  stSudowoodo                    <- stealthrockcount*Sudowoodo  
  stSwampert                      <- stealthrockcount*Swampert     
  stTerrakion                <- stealthrockcount*Terrakion
  stTorkoal                   <- stealthrockcount*Torkoal    
  stTorterra                   <- stealthrockcount*Torterra        
  stTyranitar                <- stealthrockcount*Tyranitar
  stTyrantrum                 <- stealthrockcount*Tyrantrum     
  stUxie                       <- stealthrockcount*Uxie        
  stWigglytuff               <- stealthrockcount*Wigglytuff
  stWormadamSandy            <- stealthrockcount*WormadamSandy         
  stWormadamTrash             <- stealthrockcount*WormadamTrash         
  stWormadam     <- stealthrockcount*Wormadam
options(max.print=1000000)
probit1 <- glm(outcome ~ stealthrockcount + spikescount + toxspikecount + stickywebcount + defogcount + rapidspincount + dragontailcount + roarcount + whirlwindcount, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),])
probit2 <- glm(outcome ~ stealthrockcount + spikescount +sp2 + toxspikecount + toxsp2+ stickywebcount + defogcount + fog2+ rapidspincount + rapid2+ dragontailcount +dt2 + roarcount + roar2+whirlwindcount + whirl2, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),])
probit3 <- glm(outcome ~ 
Abomasnow+  
Absol+ 
Accelgor+ 
Aerodactyl+ 
Aggron+ 
Alakazam+ 
Alomomola+ 
Altaria+ 
Ambipom+ 
Amoonguss+ 
Ampharos+ 
Arbok+ 
Arcanine+ 
Archeops+ 
Ariados+ 
Armaldo+ 
Aromatisse+ 
Articuno+ 
Audino+ 
Aurorus+ 
Avalugg+ 
Azelf+ 
Azumarill+ 
Banette+ 
Barbaracle+ 
Basculin+ 
Bastiodon+ 
Beartic+ 
Beautifly+ 
Beedrill+ 
Beheeyem+ 
Bellossom+ 
Bibarel+ 
Bisharp+ 
Blastoise+ 
Blissey+ 
Bouffalant+ 
Braviary+ 
Breloom+ 
Bronzong+ 
Butterfree+ 
Cacturne+ 
Camerupt+ 
Carbink+ 
Carnivine+ 
Carracosta+ 
Castform+ 
Celebi+ 
Chandelure+ 
Chansey +  
Charizard +  
Chatot +  
Cherrim +  
Chesnaught +  
Chimecho +  
Cinccino +  
Clawitzer +  
Claydol +  
Clefable +  
Clefairy +  
Cloyster +  
Cobalion +  
Cofagrigus +  
Combusken +  
Conkeldurr +  
Corsola +  
Cradily +  
Crawdaunt +  
Cresselia +  
Crobat +  
Crustle +  
Cryogonal +  
Darmanitan +  
Dedenne +  
Delcatty +  
Delibird +  
Delphox +  
Dewgong +  
Diancie +  
Diggersby +  
Ditto +  
Dodrio +  
Donphan +  
Doublade +  
Dragalge +  
Dragonair +  
Dragonite +  
Drapion +  
Drifblim +  
Druddigon +  
Dugtrio +  
Dunsparce +  
Duosion +  
Durant +  
Dusclops +  
Dusknoir +  
Dustox +  
Eelektross +  
Electivire +  
Electrode +  
Emboar +  
Emolga +  
Empoleon +  
Entei +  
Escavalier +  
Espeon +  
Excadrill +  
Exeggutor +  
Exploud +  
Farfetchd +  
Fearow +  
Feraligatr +  
Ferroseed +  
Ferrothorn +  
Flareon +  
Fletchinder +  
Floatzel +  
Florges +  
Flygon +  
Forretress +  
Fraxure +  
Froslass +  
Furfrou +  
Furret +  
Gabite +  
Gallade +  
Galvantula +  
Garbodor +  
Garchomp +  
Gardevoir +  
Gastrodon +  
Gengar +  
Gigalith +  
Girafarig +  
Glaceon +  
Glalie +  
Gligar +  
Gliscor +  
Gogoat +  
Golbat +  
Golduck +  
Golem +  
Golurk +  
Goodra +  
Gorebyss +  
Gothitelle +  
Gourgeist +  
Granbull +  
Grumpig +  
Gurdurr +  
Gyarados +  
Hariyama +  
Haunter +  
Hawlucha +  
Haxorus +  
Heatmor +  
Heatran +  
Heliolisk +  
Heracross +  
Hippowdon +  
Hitmonchan +  
Hitmonlee +  
Hitmontop +  
Honchkrow +  
Hoopa +  
HoopaU +  
Houndoom +  
Huntail +  
Hydreigon +  
Hypno +  
Illumise +  
Infernape +  
Jellicent +  
Jirachi +  
Jolteon +  
Jumpluff +  
Jynx +  
Kabutops +  
Kadabra +  
Kangaskhan +  
Kecleon +  
Keldeo +  
Kingdra +  
Kingler +  
Klang +  
Klefki +  
Klinklang +  
Kricketune +  
Krokorok +  
Krookodile +  
Kyurem +  
KyuremB +  
LandorusT +  
Lanturn +  
Lapras +  
Latias +  
Latios +  
Leafeon +  
Leavanny +  
Ledian +  
Lickilicky +  
Liepard +  
Lilligant +  
Linoone +  
Lopunny +  
Lucario +  
Ludicolo +  
Lumineon +  
Lunatone +  
Luvdisc +  
Luxray +  
Machamp +  
Machoke +  
Magcargo +  
Magmortar +  
Magneton +  
Magnezone +  
Malamar +  
Mamoswine +  
Manaphy +  
Mandibuzz +  
Manectric +  
Mantine +  
Maractus +  
Marowak +  
Masquerain +  
Mawile +  
Medicham +  
Meganium +  
Meloetta +  
Meowstic +  
Mesprit +  
Metagross +  
Metang +  
Mew +  
Mienshao +  
Mightyena +  
Milotic +  
Miltank +  
Minun +  
Misdreavus +  
Mismagius +  
Moltres +  
Monferno +  
Mothim +  
MrMime +  
Muk +  
Murkrow +  
Musharna +  
Nidoking +  
Nidoqueen +  
Ninetales +  
Ninjask +  
Noctowl +  
Noivern +  
Octillery +  
Omastar +  
Pachirisu +  
Pangoro +  
Parasect +  
Pawniard +  
Pelipper +  
Persian +  
Phione +  
Pidgeot +  
Piloswine +  
Pinsir +  
Plusle +  
Politoed +  
Poliwrath +  
PorygonZ +  
Porygon2 +  
Primeape +  
Prinplup +  
Probopass +  
Purugly +  
Pyroar +  
Quagsire +  
Quilladin +  
Qwilfish +  
Raichu +  
Raikou +  
Rampardos +  
Rapidash +  
Raticate +  
Regice +  
Regigigas +  
Regirock +  
Registeel +  
Relicanth +  
Reuniclus +  
Rhydon +  
Rhyperior +  
Roselia +  
Roserade +  
Rotom +  
RotomC +  
RotomF +  
RotomH +  
RotomS +  
RotomW +  
Sableye +  
Salamence +  
Samurott +  
Sandslash +  
Sawk +  
Sawsbuck +  
Sceptile +  
Scizor +  
Scolipede +  
Scrafty +  
Scyther +  
Seaking +  
Seismitoad +  
Serperior +  
Servine +  
Seviper +  
Sharpedo +  
Shaymin +  
Shedinja +  
Shiftry +  
Shuckle +  
Sigilyph +  
Simipour +  
Simisage +  
Simisear +  
Skarmory +  
Skuntank +  
Slaking +  
Slowbro +  
Slowking +  
Slurpuff +  
Smeargle +  
Sneasel +  
Snorlax +  
Solrock +  
Spinda +  
Spiritomb +  
Stantler +  
Staraptor +  
Starmie +  
Steelix +  
Stoutland +  
Stunfisk +  
Sudowoodo +  
Suicune +  
Sunflora +  
Swalot +  
Swampert +  
Swanna +  
Swellow +  
Swoobat +  
Sylveon +  
Talonflame +  
Tangela +  
Tangrowth +  
Tauros +  
Tentacruel +  
Terrakion +  
Throh +  
Thundurus +  
ThundurusT +  
Togekiss +  
Togetic +  
Torkoal +  
Tornadus +  
TornadusT +  
Torterra +  
Toxicroak +  
Trevenant +  
Tropius +  
Typhlosion +  
Tyranitar +  
Tyrantrum +  
Umbreon +  
Unfezant +  
Unown +  
Ursaring +  
Uxie +  
Vanilluxe +  
Vaporeon +  
Venomoth +  
Venusaur +  
Vespiquen +  
Vibrava +  
Victini +  
Victreebel +  
Vigoroth +  
Vileplume +  
Virizion +  
Vivillon +  
Volbeat +  
Volcarona +  
Vullaby +  
Wailord +  
Walrein +  
Wartortle +  
Watchog +  
Weavile +  
Weezing +  
Whimsicott +  
Whiscash +  
Wigglytuff +  
Wobbuffet +  
Wormadam +  
WormadamSandy +  
WormadamTrash +  
Xatu +  
Yanmega +  
Zangoose+      
Zapdos +
Zebstrika+ 
Zoroark+ 
Zweilous+ 
Zygarde, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),] )
probit4 <- glm(outcome ~
                    + Absolite
                  +Aerodactylite
                  +Aggronite
                  +Alakazite
                  +Altarianite
                  +Ampharosite
                  +Audinite
                  +Banettite
                  +Beedrillite
                  +Blastoisinite
                  +Cameruptite
                  +Charizarditex
                  +Charizarditey
                  +Diancite
                  +Galladite
                  +Garchompite
                  +Gardevoirite
                  +Glalitite
                  +Gyaradosite
                  +Heracronite
                  +Houndoominite
                  +Latiasite
                  +Latiosite
                  +Lopunnite
                  +Manectite
                  +Medichamite
                  +Metagrossite
                  +Pidgeotite
                  +Pinsirite
                  +Sablenite
                  +Sceptilite
                  +Scizorite
                  +Sharpedonite
                  +Slowbronite
                  +Steelixite
                  +Swampertite
                  +Tyranitarite
                  +Venusaurite, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),] )
probit5 <- glm(outcome ~Abomasnow+  
                        Absol+ 
                        Accelgor+ 
                        Aerodactyl+ 
                        Aggron+ 
                        Alakazam+ 
                        Alomomola+ 
                        Altaria+ 
                        Ambipom+ 
                        Amoonguss+ 
                        Ampharos+ 
                        Arbok+ 
                        Arcanine+ 
                        Archeops+ 
                        Ariados+ 
                        Armaldo+ 
                        Aromatisse+ 
                        Articuno+ 
                        Audino+ 
                        Aurorus+ 
                        Avalugg+ 
                        Azelf+ 
                        Azumarill+ 
                        Banette+ 
                        Barbaracle+ 
                        Basculin+ 
                        Bastiodon+ 
                        Beartic+ 
                        Beautifly+ 
                        Beedrill+ 
                        Beheeyem+ 
                        Bellossom+ 
                        Bibarel+ 
                        Bisharp+ 
                        Blastoise+ 
                        Blissey+ 
                        Bouffalant+ 
                        Braviary+ 
                        Breloom+ 
                        Bronzong+ 
                        Butterfree+ 
                        Cacturne+ 
                        Camerupt+ 
                        Carbink+ 
                        Carnivine+ 
                        Carracosta+ 
                        Castform+ 
                        Celebi+ 
                        Chandelure+ 
                        Chansey +  
                        Charizard +  
                        Chatot +  
                        Cherrim +  
                        Chesnaught +  
                        Chimecho +  
                        Cinccino +  
                        Clawitzer +  
                        Claydol +  
                        Clefable +  
                        Clefairy +  
                        Cloyster +  
                        Cobalion +  
                        Cofagrigus +  
                        Combusken +  
                        Conkeldurr +  
                        Corsola +  
                        Cradily +  
                        Crawdaunt +  
                        Cresselia +  
                        Crobat +  
                        Crustle +  
                        Cryogonal +  
                        Darmanitan +  
                        Dedenne +  
                        Delcatty +  
                        Delibird +  
                        Delphox +  
                        Dewgong +  
                        Diancie +  
                        Diggersby +  
                        Ditto +  
                        Dodrio +  
                        Donphan +  
                        Doublade +  
                        Dragalge +  
                        Dragonair +  
                        Dragonite +  
                        Drapion +  
                        Drifblim +  
                        Druddigon +  
                        Dugtrio +  
                        Dunsparce +  
                        Duosion +  
                        Durant +  
                        Dusclops +  
                        Dusknoir +  
                        Dustox +  
                        Eelektross +  
                        Electivire +  
                        Electrode +  
                        Emboar +  
                        Emolga +  
                        Empoleon +  
                        Entei +  
                        Escavalier +  
                        Espeon +  
                        Excadrill +  
                        Exeggutor +  
                        Exploud +  
                        Farfetchd +  
                        Fearow +  
                        Feraligatr +  
                        Ferroseed +  
                        Ferrothorn +  
                        Flareon +  
                        Fletchinder +  
                        Floatzel +  
                        Florges +  
                        Flygon +  
                        Forretress +  
                        Fraxure +  
                        Froslass +  
                        Furfrou +  
                        Furret +  
                        Gabite +  
                        Gallade +  
                        Galvantula +  
                        Garbodor +  
                        Garchomp +  
                        Gardevoir +  
                        Gastrodon +  
                        Gengar +  
                        Gigalith +  
                        Girafarig +  
                        Glaceon +  
                        Glalie +  
                        Gligar +  
                        Gliscor +  
                        Gogoat +  
                        Golbat +  
                        Golduck +  
                        Golem +  
                        Golurk +  
                        Goodra +  
                        Gorebyss +  
                        Gothitelle +  
                        Gourgeist +  
                        Granbull +  
                        Grumpig +  
                        Gurdurr +  
                        Gyarados +  
                        Hariyama +  
                        Haunter +  
                        Hawlucha +  
                        Haxorus +  
                        Heatmor +  
                        Heatran +  
                        Heliolisk +  
                        Heracross +  
                        Hippowdon +  
                        Hitmonchan +  
                        Hitmonlee +  
                        Hitmontop +  
                        Honchkrow +  
                        Hoopa +  
                        HoopaU +  
                        Houndoom +  
                        Huntail +  
                        Hydreigon +  
                        Hypno +  
                        Illumise +  
                        Infernape +  
                        Jellicent +  
                        Jirachi +  
                        Jolteon +  
                        Jumpluff +  
                        Jynx +  
                        Kabutops +  
                        Kadabra +  
                        Kangaskhan +  
                        Kecleon +  
                        Keldeo +  
                        Kingdra +  
                        Kingler +  
                        Klang +  
                        Klefki +  
                        Klinklang +  
                        Kricketune +  
                        Krokorok +  
                        Krookodile +  
                        Kyurem +  
                        KyuremB +  
                        LandorusT +  
                        Lanturn +  
                        Lapras +  
                        Latias +  
                        Latios +  
                        Leafeon +  
                        Leavanny +  
                        Ledian +  
                        Lickilicky +  
                        Liepard +  
                        Lilligant +  
                        Linoone +  
                        Lopunny +  
                        Lucario +  
                        Ludicolo +  
                        Lumineon +  
                        Lunatone +  
                        Luvdisc +  
                        Luxray +  
                        Machamp +  
                        Machoke +  
                        Magcargo +  
                        Magmortar +  
                        Magneton +  
                        Magnezone +  
                        Malamar +  
                        Mamoswine +  
                        Manaphy +  
                        Mandibuzz +  
                        Manectric +  
                        Mantine +  
                        Maractus +  
                        Marowak +  
                        Masquerain +  
                        Mawile +  
                        Medicham +  
                        Meganium +  
                        Meloetta +  
                        Meowstic +  
                        Mesprit +  
                        Metagross +  
                        Metang +  
                        Mew +  
                        Mienshao +  
                        Mightyena +  
                        Milotic +  
                        Miltank +  
                        Minun +  
                        Misdreavus +  
                        Mismagius +  
                        Moltres +  
                        Monferno +  
                        Mothim +  
                        MrMime +  
                        Muk +  
                        Murkrow +  
                        Musharna +  
                        Nidoking +  
                        Nidoqueen +  
                        Ninetales +  
                        Ninjask +  
                        Noctowl +  
                        Noivern +  
                        Octillery +  
                        Omastar +  
                        Pachirisu +  
                        Pangoro +  
                        Parasect +  
                        Pawniard +  
                        Pelipper +  
                        Persian +  
                        Phione +  
                        Pidgeot +  
                        Piloswine +  
                        Pinsir +  
                        Plusle +  
                        Politoed +  
                        Poliwrath +  
                        PorygonZ +  
                        Porygon2 +  
                        Primeape +  
                        Prinplup +  
                        Probopass +  
                        Purugly +  
                        Pyroar +  
                        Quagsire +  
                        Quilladin +  
                        Qwilfish +  
                        Raichu +  
                        Raikou +  
                        Rampardos +  
                        Rapidash +  
                        Raticate +  
                        Regice +  
                        Regigigas +  
                        Regirock +  
                        Registeel +  
                        Relicanth +  
                        Reuniclus +  
                        Rhydon +  
                        Rhyperior +  
                        Roselia +  
                        Roserade +  
                        Rotom +  
                        RotomC +  
                        RotomF +  
                        RotomH +  
                        RotomS +  
                        RotomW +  
                        Sableye +  
                        Salamence +  
                        Samurott +  
                        Sandslash +  
                        Sawk +  
                        Sawsbuck +  
                        Sceptile +  
                        Scizor +  
                        Scolipede +  
                        Scrafty +  
                        Scyther +  
                        Seaking +  
                        Seismitoad +  
                        Serperior +  
                        Servine +  
                        Seviper +  
                        Sharpedo +  
                        Shaymin +  
                        Shedinja +  
                        Shiftry +  
                        Shuckle +  
                        Sigilyph +  
                        Simipour +  
                        Simisage +  
                        Simisear +  
                        Skarmory +  
                        Skuntank +  
                        Slaking +  
                        Slowbro +  
                        Slowking +  
                        Slurpuff +  
                        Smeargle +  
                        Sneasel +  
                        Snorlax +  
                        Solrock +  
                        Spinda +  
                        Spiritomb +  
                        Stantler +  
                        Staraptor +  
                        Starmie +  
                        Steelix +  
                        Stoutland +  
                        Stunfisk +  
                        Sudowoodo +  
                        Suicune +  
                        Sunflora +  
                        Swalot +  
                        Swampert +  
                        Swanna +  
                        Swellow +  
                        Swoobat +  
                        Sylveon +  
                        Talonflame +  
                        Tangela +  
                        Tangrowth +  
                        Tauros +  
                        Tentacruel +  
                        Terrakion +  
                        Throh +  
                        Thundurus +  
                        ThundurusT +  
                        Togekiss +  
                        Togetic +  
                        Torkoal +  
                        Tornadus +  
                        TornadusT +  
                        Torterra +  
                        Toxicroak +  
                        Trevenant +  
                        Tropius +  
                        Typhlosion +  
                        Tyranitar +  
                        Tyrantrum +  
                        Umbreon +  
                        Unfezant +  
                        Unown +  
                        Ursaring +  
                        Uxie +  
                        Vanilluxe +  
                        Vaporeon +  
                        Venomoth +  
                        Venusaur +  
                        Vespiquen +  
                        Vibrava +  
                        Victini +  
                        Victreebel +  
                        Vigoroth +  
                        Vileplume +  
                        Virizion +  
                        Vivillon +  
                        Volbeat +  
                        Volcarona +  
                        Vullaby +  
                        Wailord +  
                        Walrein +  
                        Wartortle +  
                        Watchog +  
                        Weavile +  
                        Weezing +  
                        Whimsicott +  
                        Whiscash +  
                        Wigglytuff +  
                        Wobbuffet +  
                        Wormadam +  
                        WormadamSandy +  
                        WormadamTrash +  
                        Xatu +  
                        Yanmega +  
                        Zangoose+      
                        Zapdos +
                        Zebstrika+ 
                        Zoroark+ 
                        Zweilous+ 
                        Zygarde + 
                        Abomasite + 
                    + Absolite
                  +Aerodactylite
                  +Aggronite
                  +Alakazite
                  +Altarianite
                  +Ampharosite
                  +Audinite
                  +Banettite
                  +Beedrillite
                  +Blastoisinite
                  +Cameruptite
                  +Charizarditex
                  +Charizarditey
                  +Diancite
                  +Galladite
                  +Garchompite
                  +Gardevoirite
                  +Glalitite
                  +Gyaradosite
                  +Heracronite
                  +Houndoominite
                  +Latiasite
                  +Latiosite
                  +Lopunnite
                  +Manectite
                  +Medichamite
                  +Metagrossite
                  +Pidgeotite
                  +Pinsirite
                  +Sablenite
                  +Sceptilite
                  +Scizorite
                  +Sharpedonite
                  +Slowbronite
                  +Steelixite
                  +Swampertite
                  +Tyranitarite
                  +Venusaurite, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),] )
probit6 <- glm(outcome ~stealthrockcount + spikescount +sp2 + toxspikecount + toxsp2+ stickywebcount + defogcount + fog2+ rapidspincount + rapid2+ dragontailcount +dt2 + roarcount + roar2+whirlwindcount + whirl2Abomasnow+  
                        Absol+ 
                        Accelgor+ 
                        Aerodactyl+ 
                        Aggron+ 
                        Alakazam+ 
                        Alomomola+ 
                        Altaria+ 
                        Ambipom+ 
                        Amoonguss+ 
                        Ampharos+ 
                        Arbok+ 
                        Arcanine+ 
                        Archeops+ 
                        Ariados+ 
                        Armaldo+ 
                        Aromatisse+ 
                        Articuno+ 
                        Audino+ 
                        Aurorus+ 
                        Avalugg+ 
                        Azelf+ 
                        Azumarill+ 
                        Banette+ 
                        Barbaracle+ 
                        Basculin+ 
                        Bastiodon+ 
                        Beartic+ 
                        Beautifly+ 
                        Beedrill+ 
                        Beheeyem+ 
                        Bellossom+ 
                        Bibarel+ 
                        Bisharp+ 
                        Blastoise+ 
                        Blissey+ 
                        Bouffalant+ 
                        Braviary+ 
                        Breloom+ 
                        Bronzong+ 
                        Butterfree+ 
                        Cacturne+ 
                        Camerupt+ 
                        Carbink+ 
                        Carnivine+ 
                        Carracosta+ 
                        Castform+ 
                        Celebi+ 
                        Chandelure+ 
                        Chansey +  
                        Charizard +  
                        Chatot +  
                        Cherrim +  
                        Chesnaught +  
                        Chimecho +  
                        Cinccino +  
                        Clawitzer +  
                        Claydol +  
                        Clefable +  
                        Clefairy +  
                        Cloyster +  
                        Cobalion +  
                        Cofagrigus +  
                        Combusken +  
                        Conkeldurr +  
                        Corsola +  
                        Cradily +  
                        Crawdaunt +  
                        Cresselia +  
                        Crobat +  
                        Crustle +  
                        Cryogonal +  
                        Darmanitan +  
                        Dedenne +  
                        Delcatty +  
                        Delibird +  
                        Delphox +  
                        Dewgong +  
                        Diancie +  
                        Diggersby +  
                        Ditto +  
                        Dodrio +  
                        Donphan +  
                        Doublade +  
                        Dragalge +  
                        Dragonair +  
                        Dragonite +  
                        Drapion +  
                        Drifblim +  
                        Druddigon +  
                        Dugtrio +  
                        Dunsparce +  
                        Duosion +  
                        Durant +  
                        Dusclops +  
                        Dusknoir +  
                        Dustox +  
                        Eelektross +  
                        Electivire +  
                        Electrode +  
                        Emboar +  
                        Emolga +  
                        Empoleon +  
                        Entei +  
                        Escavalier +  
                        Espeon +  
                        Excadrill +  
                        Exeggutor +  
                        Exploud +  
                        Farfetchd +  
                        Fearow +  
                        Feraligatr +  
                        Ferroseed +  
                        Ferrothorn +  
                        Flareon +  
                        Fletchinder +  
                        Floatzel +  
                        Florges +  
                        Flygon +  
                        Forretress +  
                        Fraxure +  
                        Froslass +  
                        Furfrou +  
                        Furret +  
                        Gabite +  
                        Gallade +  
                        Galvantula +  
                        Garbodor +  
                        Garchomp +  
                        Gardevoir +  
                        Gastrodon +  
                        Gengar +  
                        Gigalith +  
                        Girafarig +  
                        Glaceon +  
                        Glalie +  
                        Gligar +  
                        Gliscor +  
                        Gogoat +  
                        Golbat +  
                        Golduck +  
                        Golem +  
                        Golurk +  
                        Goodra +  
                        Gorebyss +  
                        Gothitelle +  
                        Gourgeist +  
                        Granbull +  
                        Grumpig +  
                        Gurdurr +  
                        Gyarados +  
                        Hariyama +  
                        Haunter +  
                        Hawlucha +  
                        Haxorus +  
                        Heatmor +  
                        Heatran +  
                        Heliolisk +  
                        Heracross +  
                        Hippowdon +  
                        Hitmonchan +  
                        Hitmonlee +  
                        Hitmontop +  
                        Honchkrow +  
                        Hoopa +  
                        HoopaU +  
                        Houndoom +  
                        Huntail +  
                        Hydreigon +  
                        Hypno +  
                        Illumise +  
                        Infernape +  
                        Jellicent +  
                        Jirachi +  
                        Jolteon +  
                        Jumpluff +  
                        Jynx +  
                        Kabutops +  
                        Kadabra +  
                        Kangaskhan +  
                        Kecleon +  
                        Keldeo +  
                        Kingdra +  
                        Kingler +  
                        Klang +  
                        Klefki +  
                        Klinklang +  
                        Kricketune +  
                        Krokorok +  
                        Krookodile +  
                        Kyurem +  
                        KyuremB +  
                        LandorusT +  
                        Lanturn +  
                        Lapras +  
                        Latias +  
                        Latios +  
                        Leafeon +  
                        Leavanny +  
                        Ledian +  
                        Lickilicky +  
                        Liepard +  
                        Lilligant +  
                        Linoone +  
                        Lopunny +  
                        Lucario +  
                        Ludicolo +  
                        Lumineon +  
                        Lunatone +  
                        Luvdisc +  
                        Luxray +  
                        Machamp +  
                        Machoke +  
                        Magcargo +  
                        Magmortar +  
                        Magneton +  
                        Magnezone +  
                        Malamar +  
                        Mamoswine +  
                        Manaphy +  
                        Mandibuzz +  
                        Manectric +  
                        Mantine +  
                        Maractus +  
                        Marowak +  
                        Masquerain +  
                        Mawile +  
                        Medicham +  
                        Meganium +  
                        Meloetta +  
                        Meowstic +  
                        Mesprit +  
                        Metagross +  
                        Metang +  
                        Mew +  
                        Mienshao +  
                        Mightyena +  
                        Milotic +  
                        Miltank +  
                        Minun +  
                        Misdreavus +  
                        Mismagius +  
                        Moltres +  
                        Monferno +  
                        Mothim +  
                        MrMime +  
                        Muk +  
                        Murkrow +  
                        Musharna +  
                        Nidoking +  
                        Nidoqueen +  
                        Ninetales +  
                        Ninjask +  
                        Noctowl +  
                        Noivern +  
                        Octillery +  
                        Omastar +  
                        Pachirisu +  
                        Pangoro +  
                        Parasect +  
                        Pawniard +  
                        Pelipper +  
                        Persian +  
                        Phione +  
                        Pidgeot +  
                        Piloswine +  
                        Pinsir +  
                        Plusle +  
                        Politoed +  
                        Poliwrath +  
                        PorygonZ +  
                        Porygon2 +  
                        Primeape +  
                        Prinplup +  
                        Probopass +  
                        Purugly +  
                        Pyroar +  
                        Quagsire +  
                        Quilladin +  
                        Qwilfish +  
                        Raichu +  
                        Raikou +  
                        Rampardos +  
                        Rapidash +  
                        Raticate +  
                        Regice +  
                        Regigigas +  
                        Regirock +  
                        Registeel +  
                        Relicanth +  
                        Reuniclus +  
                        Rhydon +  
                        Rhyperior +  
                        Roselia +  
                        Roserade +  
                        Rotom +  
                        RotomC +  
                        RotomF +  
                        RotomH +  
                        RotomS +  
                        RotomW +  
                        Sableye +  
                        Salamence +  
                        Samurott +  
                        Sandslash +  
                        Sawk +  
                        Sawsbuck +  
                        Sceptile +  
                        Scizor +  
                        Scolipede +  
                        Scrafty +  
                        Scyther +  
                        Seaking +  
                        Seismitoad +  
                        Serperior +  
                        Servine +  
                        Seviper +  
                        Sharpedo +  
                        Shaymin +  
                        Shedinja +  
                        Shiftry +  
                        Shuckle +  
                        Sigilyph +  
                        Simipour +  
                        Simisage +  
                        Simisear +  
                        Skarmory +  
                        Skuntank +  
                        Slaking +  
                        Slowbro +  
                        Slowking +  
                        Slurpuff +  
                        Smeargle +  
                        Sneasel +  
                        Snorlax +  
                        Solrock +  
                        Spinda +  
                        Spiritomb +  
                        Stantler +  
                        Staraptor +  
                        Starmie +  
                        Steelix +  
                        Stoutland +  
                        Stunfisk +  
                        Sudowoodo +  
                        Suicune +  
                        Sunflora +  
                        Swalot +  
                        Swampert +  
                        Swanna +  
                        Swellow +  
                        Swoobat +  
                        Sylveon +  
                        Talonflame +  
                        Tangela +  
                        Tangrowth +  
                        Tauros +  
                        Tentacruel +  
                        Terrakion +  
                        Throh +  
                        Thundurus +  
                        ThundurusT +  
                        Togekiss +  
                        Togetic +  
                        Torkoal +  
                        Tornadus +  
                        TornadusT +  
                        Torterra +  
                        Toxicroak +  
                        Trevenant +  
                        Tropius +  
                        Typhlosion +  
                        Tyranitar +  
                        Tyrantrum +  
                        Umbreon +  
                        Unfezant +  
                        Unown +  
                        Ursaring +  
                        Uxie +  
                        Vanilluxe +  
                        Vaporeon +  
                        Venomoth +  
                        Venusaur +  
                        Vespiquen +  
                        Vibrava +  
                        Victini +  
                        Victreebel +  
                        Vigoroth +  
                        Vileplume +  
                        Virizion +  
                        Vivillon +  
                        Volbeat +  
                        Volcarona +  
                        Vullaby +  
                        Wailord +  
                        Walrein +  
                        Wartortle +  
                        Watchog +  
                        Weavile +  
                        Weezing +  
                        Whimsicott +  
                        Whiscash +  
                        Wigglytuff +  
                        Wobbuffet +  
                        Wormadam +  
                        WormadamSandy +  
                        WormadamTrash +  
                        Xatu +  
                        Yanmega +  
                        Zangoose+      
                        Zapdos +
                        Zebstrika+ 
                        Zoroark+ 
                        Zweilous+ 
                        Zygarde + 
                        Abomasite + 
                    + Absolite
                  +Aerodactylite
                  +Aggronite
                  +Alakazite
                  +Altarianite
                  +Ampharosite
                  +Audinite
                  +Banettite
                  +Beedrillite
                  +Blastoisinite
                  +Cameruptite
                  +Charizarditex
                  +Charizarditey
                  +Diancite
                  +Galladite
                  +Garchompite
                  +Gardevoirite
                  +Glalitite
                  +Gyaradosite
                  +Heracronite
                  +Houndoominite
                  +Latiasite
                  +Latiosite
                  +Lopunnite
                  +Manectite
                  +Medichamite
                  +Metagrossite
                  +Pidgeotite
                  +Pinsirite
                  +Sablenite
                  +Sceptilite
                  +Scizorite
                  +Sharpedonite
                  +Slowbronite
                  +Steelixite
                  +Swampertite
                  +Tyranitarite
                  +Venusaurite, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),] )
probit7 <- glm(outcome ~ stAerodactyl +
                           stAggron +
                           stArcheops+       
                           stArmaldo +
                           stAurorus +
                           stAzelf    +     
                           stBarbaracle+          
                           stBastiodon  +          
                           stBibarel     +      
                           stBisharp      +      
                           stBlissey       +       
                           stBronzong       +   
                           stCamerupt        +    
                           stCarbink          +        
                           stCarracosta     +
                           stCelebi          +  
                           stChansey          +       
                           stClaydol           +
                           stClefable           + 
                           stClefairy            +     
                           stCobalion       +
                           stCorsola         +  
                           stCradily          +        
                           stCrustle         +
                           stDiancie      +  
                           stDonphan       +           
                           stDruddigon      +
                           stDugtrio         +   
                           stDunsparce        +        
                           stEmpoleon         +
                           stExcadrill         +   
                           stFerroseed          +      
                           stFerrothorn      +
                           stForretress       +    
                           stGabite            +      
                           stGarchomp        +
                           stGigalith         +   
                           stGligar            +       
                           stGliscor         +
                           stGolem            + 
                           stGolurk            +       
                           stHeatran          +
                           stHippowdon         +   
                           stInfernape          +  
                           stJirachi         +
                           stKabutops         +   
                           stKecleon           +       
                           stKrokorok        +
                           stKrookodile       +    
                           stLunatone          +   
                           stMagcargo      +
                           stMamoswine      +     
                           stMarowak         +         
                           stMawile          +
                           stMesprit          + 
                           stMetagross         +   
                           stMetang      +
                           stMew          +   
                           stMiltank       +          
                           stMonferno   +
                           stNidoking    +         
                           stNidoqueen    +    
                           stOmastar       +   
                           stPawniard       +      
                           stPiloswine       +     
                           stPinsir           + 
                           stPrinplup          +   
                           stProbopass          +  
                           stRampardos       +
                           stRegirock         +    
                           stRegisteel         +   
                           stRelicanth        +
                           stRhydon            + 
                           stRhyperior          +  
                           stSandslash         +
                           stSeismitoad          + 
                           stShuckle              +   
                           stSkarmory       +
                           stSolrock         +    
                           stSteelix          +       
                           stStunfisk          + 
                           stSudowoodo          +  
                           stSwampert            +     
                           stTerrakion      +
                           stTorkoal         +    
                           stTorterra         +        
                           stTyranitar      +
                           stTyrantrum       +     
                           stUxie             +        
                           stWigglytuff     +
                           stWormadamSandy  +         
                           stWormadamTrash   +         
                           stWormadam + spikescount +sp2 + toxspikecount + toxsp2+ stickywebcount + defogcount + fog2+ rapidspincount + rapid2+ dragontailcount +dt2 + roarcount + roar2+whirlwindcount + whirl2Abomasnow+  
                        Absol+ 
                        Accelgor+ 
                        Aerodactyl+ 
                        Aggron+ 
                        Alakazam+ 
                        Alomomola+ 
                        Altaria+ 
                        Ambipom+ 
                        Amoonguss+ 
                        Ampharos+ 
                        Arbok+ 
                        Arcanine+ 
                        Archeops+ 
                        Ariados+ 
                        Armaldo+ 
                        Aromatisse+ 
                        Articuno+ 
                        Audino+ 
                        Aurorus+ 
                        Avalugg+ 
                        Azelf+ 
                        Azumarill+ 
                        Banette+ 
                        Barbaracle+ 
                        Basculin+ 
                        Bastiodon+ 
                        Beartic+ 
                        Beautifly+ 
                        Beedrill+ 
                        Beheeyem+ 
                        Bellossom+ 
                        Bibarel+ 
                        Bisharp+ 
                        Blastoise+ 
                        Blissey+ 
                        Bouffalant+ 
                        Braviary+ 
                        Breloom+ 
                        Bronzong+ 
                        Butterfree+ 
                        Cacturne+ 
                        Camerupt+ 
                        Carbink+ 
                        Carnivine+ 
                        Carracosta+ 
                        Castform+ 
                        Celebi+ 
                        Chandelure+ 
                        Chansey +  
                        Charizard +  
                        Chatot +  
                        Cherrim +  
                        Chesnaught +  
                        Chimecho +  
                        Cinccino +  
                        Clawitzer +  
                        Claydol +  
                        Clefable +  
                        Clefairy +  
                        Cloyster +  
                        Cobalion +  
                        Cofagrigus +  
                        Combusken +  
                        Conkeldurr +  
                        Corsola +  
                        Cradily +  
                        Crawdaunt +  
                        Cresselia +  
                        Crobat +  
                        Crustle +  
                        Cryogonal +  
                        Darmanitan +  
                        Dedenne +  
                        Delcatty +  
                        Delibird +  
                        Delphox +  
                        Dewgong +  
                        Diancie +  
                        Diggersby +  
                        Ditto +  
                        Dodrio +  
                        Donphan +  
                        Doublade +  
                        Dragalge +  
                        Dragonair +  
                        Dragonite +  
                        Drapion +  
                        Drifblim +  
                        Druddigon +  
                        Dugtrio +  
                        Dunsparce +  
                        Duosion +  
                        Durant +  
                        Dusclops +  
                        Dusknoir +  
                        Dustox +  
                        Eelektross +  
                        Electivire +  
                        Electrode +  
                        Emboar +  
                        Emolga +  
                        Empoleon +  
                        Entei +  
                        Escavalier +  
                        Espeon +  
                        Excadrill +  
                        Exeggutor +  
                        Exploud +  
                        Farfetchd +  
                        Fearow +  
                        Feraligatr +  
                        Ferroseed +  
                        Ferrothorn +  
                        Flareon +  
                        Fletchinder +  
                        Floatzel +  
                        Florges +  
                        Flygon +  
                        Forretress +  
                        Fraxure +  
                        Froslass +  
                        Furfrou +  
                        Furret +  
                        Gabite +  
                        Gallade +  
                        Galvantula +  
                        Garbodor +  
                        Garchomp +  
                        Gardevoir +  
                        Gastrodon +  
                        Gengar +  
                        Gigalith +  
                        Girafarig +  
                        Glaceon +  
                        Glalie +  
                        Gligar +  
                        Gliscor +  
                        Gogoat +  
                        Golbat +  
                        Golduck +  
                        Golem +  
                        Golurk +  
                        Goodra +  
                        Gorebyss +  
                        Gothitelle +  
                        Gourgeist +  
                        Granbull +  
                        Grumpig +  
                        Gurdurr +  
                        Gyarados +  
                        Hariyama +  
                        Haunter +  
                        Hawlucha +  
                        Haxorus +  
                        Heatmor +  
                        Heatran +  
                        Heliolisk +  
                        Heracross +  
                        Hippowdon +  
                        Hitmonchan +  
                        Hitmonlee +  
                        Hitmontop +  
                        Honchkrow +  
                        Hoopa +  
                        HoopaU +  
                        Houndoom +  
                        Huntail +  
                        Hydreigon +  
                        Hypno +  
                        Illumise +  
                        Infernape +  
                        Jellicent +  
                        Jirachi +  
                        Jolteon +  
                        Jumpluff +  
                        Jynx +  
                        Kabutops +  
                        Kadabra +  
                        Kangaskhan +  
                        Kecleon +  
                        Keldeo +  
                        Kingdra +  
                        Kingler +  
                        Klang +  
                        Klefki +  
                        Klinklang +  
                        Kricketune +  
                        Krokorok +  
                        Krookodile +  
                        Kyurem +  
                        KyuremB +  
                        LandorusT +  
                        Lanturn +  
                        Lapras +  
                        Latias +  
                        Latios +  
                        Leafeon +  
                        Leavanny +  
                        Ledian +  
                        Lickilicky +  
                        Liepard +  
                        Lilligant +  
                        Linoone +  
                        Lopunny +  
                        Lucario +  
                        Ludicolo +  
                        Lumineon +  
                        Lunatone +  
                        Luvdisc +  
                        Luxray +  
                        Machamp +  
                        Machoke +  
                        Magcargo +  
                        Magmortar +  
                        Magneton +  
                        Magnezone +  
                        Malamar +  
                        Mamoswine +  
                        Manaphy +  
                        Mandibuzz +  
                        Manectric +  
                        Mantine +  
                        Maractus +  
                        Marowak +  
                        Masquerain +  
                        Mawile +  
                        Medicham +  
                        Meganium +  
                        Meloetta +  
                        Meowstic +  
                        Mesprit +  
                        Metagross +  
                        Metang +  
                        Mew +  
                        Mienshao +  
                        Mightyena +  
                        Milotic +  
                        Miltank +  
                        Minun +  
                        Misdreavus +  
                        Mismagius +  
                        Moltres +  
                        Monferno +  
                        Mothim +  
                        MrMime +  
                        Muk +  
                        Murkrow +  
                        Musharna +  
                        Nidoking +  
                        Nidoqueen +  
                        Ninetales +  
                        Ninjask +  
                        Noctowl +  
                        Noivern +  
                        Octillery +  
                        Omastar +  
                        Pachirisu +  
                        Pangoro +  
                        Parasect +  
                        Pawniard +  
                        Pelipper +  
                        Persian +  
                        Phione +  
                        Pidgeot +  
                        Piloswine +  
                        Pinsir +  
                        Plusle +  
                        Politoed +  
                        Poliwrath +  
                        PorygonZ +  
                        Porygon2 +  
                        Primeape +  
                        Prinplup +  
                        Probopass +  
                        Purugly +  
                        Pyroar +  
                        Quagsire +  
                        Quilladin +  
                        Qwilfish +  
                        Raichu +  
                        Raikou +  
                        Rampardos +  
                        Rapidash +  
                        Raticate +  
                        Regice +  
                        Regigigas +  
                        Regirock +  
                        Registeel +  
                        Relicanth +  
                        Reuniclus +  
                        Rhydon +  
                        Rhyperior +  
                        Roselia +  
                        Roserade +  
                        Rotom +  
                        RotomC +  
                        RotomF +  
                        RotomH +  
                        RotomS +  
                        RotomW +  
                        Sableye +  
                        Salamence +  
                        Samurott +  
                        Sandslash +  
                        Sawk +  
                        Sawsbuck +  
                        Sceptile +  
                        Scizor +  
                        Scolipede +  
                        Scrafty +  
                        Scyther +  
                        Seaking +  
                        Seismitoad +  
                        Serperior +  
                        Servine +  
                        Seviper +  
                        Sharpedo +  
                        Shaymin +  
                        Shedinja +  
                        Shiftry +  
                        Shuckle +  
                        Sigilyph +  
                        Simipour +  
                        Simisage +  
                        Simisear +  
                        Skarmory +  
                        Skuntank +  
                        Slaking +  
                        Slowbro +  
                        Slowking +  
                        Slurpuff +  
                        Smeargle +  
                        Sneasel +  
                        Snorlax +  
                        Solrock +  
                        Spinda +  
                        Spiritomb +  
                        Stantler +  
                        Staraptor +  
                        Starmie +  
                        Steelix +  
                        Stoutland +  
                        Stunfisk +  
                        Sudowoodo +  
                        Suicune +  
                        Sunflora +  
                        Swalot +  
                        Swampert +  
                        Swanna +  
                        Swellow +  
                        Swoobat +  
                        Sylveon +  
                        Talonflame +  
                        Tangela +  
                        Tangrowth +  
                        Tauros +  
                        Tentacruel +  
                        Terrakion +  
                        Throh +  
                        Thundurus +  
                        ThundurusT +  
                        Togekiss +  
                        Togetic +  
                        Torkoal +  
                        Tornadus +  
                        TornadusT +  
                        Torterra +  
                        Toxicroak +  
                        Trevenant +  
                        Tropius +  
                        Typhlosion +  
                        Tyranitar +  
                        Tyrantrum +  
                        Umbreon +  
                        Unfezant +  
                        Unown +  
                        Ursaring +  
                        Uxie +  
                        Vanilluxe +  
                        Vaporeon +  
                        Venomoth +  
                        Venusaur +  
                        Vespiquen +  
                        Vibrava +  
                        Victini +  
                        Victreebel +  
                        Vigoroth +  
                        Vileplume +  
                        Virizion +  
                        Vivillon +  
                        Volbeat +  
                        Volcarona +  
                        Vullaby +  
                        Wailord +  
                        Walrein +  
                        Wartortle +  
                        Watchog +  
                        Weavile +  
                        Weezing +  
                        Whimsicott +  
                        Whiscash +  
                        Wigglytuff +  
                        Wobbuffet +  
                        Wormadam +  
                        WormadamSandy +  
                        WormadamTrash +  
                        Xatu +  
                        Yanmega +  
                        Zangoose+      
                        Zapdos +
                        Zebstrika+ 
                        Zoroark+ 
                        Zweilous+ 
                        Zygarde + 
                        Abomasite + 
                    + Absolite
                  +Aerodactylite
                  +Aggronite
                  +Alakazite
                  +Altarianite
                  +Ampharosite
                  +Audinite
                  +Banettite
                  +Beedrillite
                  +Blastoisinite
                  +Cameruptite
                  +Charizarditex
                  +Charizarditey
                  +Diancite
                  +Galladite
                  +Garchompite
                  +Gardevoirite
                  +Glalitite
                  +Gyaradosite
                  +Heracronite
                  +Houndoominite
                  +Latiasite
                  +Latiosite
                  +Lopunnite
                  +Manectite
                  +Medichamite
                  +Metagrossite
                  +Pidgeotite
                  +Pinsirite
                  +Sablenite
                  +Sceptilite
                  +Scizorite
                  +Sharpedonite
                  +Slowbronite
                  +Steelixite
                  +Swampertite
                  +Tyranitarite
                  +Venusaurite, family=binomial(link="probit"), data=d1[which(d1$battle_length>0),] )
```


```{r}
library(stargazer)
```

# Preliminary Statistics 

```{r, results='asis'}
stargazer( Abomasnow,  
                        Absol,
                        Accelgor, 
                        Aerodactyl, 
                        Aggron, 
                        Alakazam, 
                        Alomomola, 
                        Altaria, 
                        Ambipom, 
                        Amoonguss, 
                        Ampharos, 
                        Arbok, 
                        Arcanine, 
                        Archeops, 
                        Ariados, 
                        Armaldo, 
                        Aromatisse, 
                        Articuno, 
                        Audino, 
                        Aurorus, 
                        Avalugg, 
                        Azelf, 
                        Azumarill, 
                        Banette, 
                        Barbaracle, 
                        Basculin, 
                        Bastiodon, 
                        Beartic, 
                        Beautifly, 
                        Beedrill, 
                        Beheeyem, 
                        Bellossom, 
                        Bibarel, 
                        Bisharp, 
                        Blastoise, 
                        Blissey, 
                        Bouffalant, 
                        Braviary, 
                        Breloom, 
                        Bronzong, 
                        Butterfree, 
                        Cacturne, 
                        Camerupt, 
                        Carbink, 
                        Carnivine, 
                        Carracosta, 
                        Castform, 
                        Celebi, 
                        Chandelure, 
                        Chansey ,  
                        Charizard ,  
                        Chatot ,  
                        Cherrim ,  
                        Chesnaught ,  
                        Chimecho ,  
                        Cinccino ,  
                        Clawitzer ,  
                        Claydol ,  
                        Clefable ,  
                        Clefairy ,  
                        Cloyster ,  
                        Cobalion ,  
                        Cofagrigus ,  
                        Combusken ,  
                        Conkeldurr ,  
                        Corsola ,  
                        Cradily ,  
                        Crawdaunt ,  
                        Cresselia ,  
                        Crobat ,  
                        Crustle ,  
                        Cryogonal ,  
                        Darmanitan ,  
                        Dedenne ,  
                        Delcatty ,  
                        Delibird ,  
                        Delphox ,  
                        Dewgong ,  
                        Diancie ,  
                        Diggersby ,  
                        Ditto ,  
                        Dodrio ,  
                        Donphan ,  
                        Doublade ,  
                        Dragalge ,  
                        Dragonair ,  
                        Dragonite ,  
                        Drapion ,  
                        Drifblim ,  
                        Druddigon ,  
                        Dugtrio ,  
                        Dunsparce ,  
                        Duosion ,  
                        Durant ,  
                        Dusclops ,  
                        Dusknoir ,  
                        Dustox ,  
                        Eelektross ,  
                        Electivire ,  
                        Electrode ,  
                        Emboar ,  
                        Emolga ,  
                        Empoleon ,  
                        Entei ,  
                        Escavalier ,  
                        Espeon ,  
                        Excadrill ,  
                        Exeggutor ,  
                        Exploud ,  
                        Farfetchd ,  
                        Fearow ,  
                        Feraligatr ,  
                        Ferroseed ,  
                        Ferrothorn ,  
                        Flareon ,  
                        Fletchinder ,  
                        Floatzel ,  
                        Florges ,  
                        Flygon ,  
                        Forretress ,  
                        Fraxure ,  
                        Froslass ,  
                        Furfrou ,  
                        Furret ,  
                        Gabite ,  
                        Gallade ,  
                        Galvantula ,  
                        Garbodor ,  
                        Garchomp ,  
                        Gardevoir ,  
                        Gastrodon ,  
                        Gengar ,  
                        Gigalith ,  
                        Girafarig ,  
                        Glaceon ,  
                        Glalie ,  
                        Gligar ,  
                        Gliscor ,  
                        Gogoat ,  
                        Golbat ,  
                        Golduck ,  
                        Golem ,  
                        Golurk ,  
                        Goodra ,  
                        Gorebyss ,  
                        Gothitelle ,  
                        Gourgeist ,  
                        Granbull ,  
                        Grumpig ,  
                        Gurdurr ,  
                        Gyarados ,  
                        Hariyama ,  
                        Haunter ,  
                        Hawlucha ,  
                        Haxorus ,  
                        Heatmor ,  
                        Heatran ,  
                        Heliolisk ,  
                        Heracross ,  
                        Hippowdon ,  
                        Hitmonchan ,  
                        Hitmonlee ,  
                        Hitmontop ,  
                        Honchkrow ,  
                        Hoopa ,  
                        HoopaU ,  
                        Houndoom ,  
                        Huntail ,  
                        Hydreigon ,  
                        Hypno ,  
                        Illumise ,  
                        Infernape ,  
                        Jellicent ,  
                        Jirachi ,  
                        Jolteon ,  
                        Jumpluff ,  
                        Jynx ,  
                        Kabutops ,  
                        Kadabra ,  
                        Kangaskhan ,  
                        Kecleon ,  
                        Keldeo ,  
                        Kingdra ,  
                        Kingler ,  
                        Klang ,  
                        Klefki ,  
                        Klinklang ,  
                        Kricketune ,  
                        Krokorok ,  
                        Krookodile ,  
                        Kyurem ,  
                        KyuremB ,  
                        LandorusT ,  
                        Lanturn ,  
                        Lapras ,  
                        Latias ,  
                        Latios ,  
                        Leafeon ,  
                        Leavanny ,  
                        Ledian ,  
                        Lickilicky ,  
                        Liepard ,  
                        Lilligant ,  
                        Linoone ,  
                        Lopunny ,  
                        Lucario ,  
                        Ludicolo ,  
                        Lumineon ,  
                        Lunatone ,  
                        Luvdisc ,  
                        Luxray ,  
                        Machamp ,  
                        Machoke ,  
                        Magcargo ,  
                        Magmortar ,  
                        Magneton ,  
                        Magnezone ,  
                        Malamar ,  
                        Mamoswine ,  
                        Manaphy ,  
                        Mandibuzz ,  
                        Manectric ,  
                        Mantine ,  
                        Maractus ,  
                        Marowak ,  
                        Masquerain ,  
                        Mawile ,  
                        Medicham ,  
                        Meganium ,  
                        Meloetta ,  
                        Meowstic ,  
                        Mesprit ,  
                        Metagross ,  
                        Metang ,  
                        Mew ,  
                        Mienshao ,  
                        Mightyena ,  
                        Milotic ,  
                        Miltank ,  
                        Minun ,  
                        Misdreavus ,  
                        Mismagius ,  
                        Moltres ,  
                        Monferno ,  
                        Mothim ,  
                        MrMime ,  
                        Muk ,  
                        Murkrow ,  
                        Musharna ,  
                        Nidoking ,  
                        Nidoqueen ,  
                        Ninetales ,  
                        Ninjask ,  
                        Noctowl ,  
                        Noivern ,  
                        Octillery ,  
                        Omastar ,  
                        Pachirisu ,  
                        Pangoro ,  
                        Parasect ,  
                        Pawniard ,  
                        Pelipper ,  
                        Persian ,  
                        Phione ,  
                        Pidgeot ,  
                        Piloswine ,  
                        Pinsir ,  
                        Plusle ,  
                        Politoed ,  
                        Poliwrath ,  
                        PorygonZ ,  
                        Porygon2 ,  
                        Primeape ,  
                        Prinplup ,  
                        Probopass ,  
                        Purugly ,  
                        Pyroar ,  
                        Quagsire ,  
                        Quilladin ,  
                        Qwilfish ,  
                        Raichu ,  
                        Raikou ,  
                        Rampardos ,  
                        Rapidash ,  
                        Raticate ,  
                        Regice ,  
                        Regigigas ,  
                        Regirock ,  
                        Registeel ,  
                        Relicanth ,  
                        Reuniclus ,  
                        Rhydon ,  
                        Rhyperior ,  
                        Roselia ,  
                        Roserade ,  
                        Rotom ,  
                        RotomC ,  
                        RotomF ,  
                        RotomH ,  
                        RotomS ,  
                        RotomW ,  
                        Sableye ,  
                        Salamence ,  
                        Samurott ,  
                        Sandslash ,  
                        Sawk ,  
                        Sawsbuck ,  
                        Sceptile ,  
                        Scizor ,  
                        Scolipede ,  
                        Scrafty ,  
                        Scyther ,  
                        Seaking ,  
                        Seismitoad ,  
                        Serperior ,  
                        Servine ,  
                        Seviper ,  
                        Sharpedo ,  
                        Shaymin ,  
                        Shedinja ,  
                        Shiftry ,  
                        Shuckle ,  
                        Sigilyph ,  
                        Simipour ,  
                        Simisage ,  
                        Simisear ,  
                        Skarmory ,  
                        Skuntank ,  
                        Slaking ,  
                        Slowbro ,  
                        Slowking ,  
                        Slurpuff ,  
                        Smeargle ,  
                        Sneasel ,  
                        Snorlax ,  
                        Solrock ,  
                        Spinda ,  
                        Spiritomb ,  
                        Stantler ,  
                        Staraptor ,  
                        Starmie ,  
                        Steelix ,  
                        Stoutland ,  
                        Stunfisk ,  
                        Sudowoodo ,  
                        Suicune ,  
                        Sunflora ,  
                        Swalot ,  
                        Swampert ,  
                        Swanna ,  
                        Swellow ,  
                        Swoobat ,  
                        Sylveon ,  
                        Talonflame ,  
                        Tangela ,  
                        Tangrowth ,  
                        Tauros ,  
                        Tentacruel ,  
                        Terrakion ,  
                        Throh ,  
                        Thundurus ,  
                        ThundurusT ,  
                        Togekiss ,  
                        Togetic ,  
                        Torkoal ,  
                        Tornadus ,  
                        TornadusT ,  
                        Torterra ,  
                        Toxicroak ,  
                        Trevenant ,  
                        Tropius ,  
                        Typhlosion ,  
                        Tyranitar ,  
                        Tyrantrum ,  
                        Umbreon ,  
                        Unfezant ,  
                        Unown ,  
                        Ursaring ,  
                        Uxie ,  
                        Vanilluxe ,  
                        Vaporeon ,  
                        Venomoth ,  
                        Venusaur ,  
                        Vespiquen ,  
                        Vibrava ,  
                        Victini ,  
                        Victreebel ,  
                        Vigoroth ,  
                        Vileplume ,  
                        Virizion ,  
                        Vivillon ,  
                        Volbeat ,  
                        Volcarona ,  
                        Vullaby ,  
                        Wailord ,  
                        Walrein ,  
                        Wartortle ,  
                        Watchog ,  
                        Weavile ,  
                        Weezing ,  
                        Whimsicott ,  
                        Whiscash ,  
                        Wigglytuff ,  
                        Wobbuffet ,  
                        Wormadam ,  
                        WormadamSandy ,  
                        WormadamTrash ,  
                        Xatu ,  
                        Yanmega ,  
                        Zangoose,      
                        Zapdos ,
                        Zebstrika, 
                        Zoroark, 
                        Zweilous, 
                        Zygarde , 
                        Abomasite , 
                     Absolite
                  ,Aerodactylite
                  ,Aggronite
                  ,Alakazite
                  ,Altarianite
                  ,Ampharosite
                  ,Audinite
                  ,Banettite
                  ,Beedrillite
                  ,Blastoisinite
                  ,Cameruptite
                  ,Charizarditex
                  ,Charizarditey
                  ,Diancite
                  ,Galladite
                  ,Garchompite
                  ,Gardevoirite
                  ,Glalitite
                  ,Gyaradosite
                  ,Heracronite
                  ,Houndoominite
                  ,Latiasite
                  ,Latiosite
                  ,Lopunnite
                  ,Manectite
                  ,Medichamite
                  ,Metagrossite
                  ,Pidgeotite
                  ,Pinsirite
                  ,Sablenite
                  ,Sceptilite
                  ,Scizorite
                  ,Sharpedonite
                  ,Slowbronite
                  ,Steelixite
                  ,Swampertite
                  ,Tyranitarite
                  ,Venusaurite, title="Pokmon and Mega Summary")
```
                  
```{r, results='asis'}
stargazer(d1 ,title="Summary Statistics")
```
The average game length is sixteen turns. However, there are a number of games in the dataset that are of zero length. To eliminate potential bias from these games, all models will be specified to only include games that lasted more than one turn. A few other facts stand out from the preliminary statistics. Specifically in regards to ranking, most observations are within the range of 1000 to 1215 elo. However, the maximum rank observed in the data is 1815. To test whether the statistics differ in higher tiers of ranking, the final model will include all battles lasting at least one turn and all ranks and one for games whose ranking is greater than the third quantile of 1215 elo. 

```{r, results='asis'}
stargazer(rank, title="Ranking")
```

```{r, results='asis'}
stargazer(probit1,probit2, title="Simple Model")
```

```{r, results='asis'}
stargazer(probit3,probit4,probit5,probit6, title="Mega Pokmon and Pokmon Models")
```

```{r, results='asis'}
stargazer(probit1,probit2,probit3,probit4,probit5,probit6, title="All Models")
```

```{r, results='asis'}
stargazer(probit6,probit7, title="Full Model and Stealth Rock Interactions")
```


